Kindly Bent To Free Us

### 2020-08-04 kindly/slides-icfp.tex
First version of the schema

\begin{frame}[fragile]{Inference and constraints}

\TODO{Show the global step-by-step process}

\begin{minted}[texcomments=true]{OCaml}
let average db subjects = 
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = {| average &gradeDB ["math";"compsci";...] |} in
  {| Dbm.add &!gradeDB "average" avg |}
\end{minted}

\section*{Conclusion}

>>>>

\begin{frame}{Inference and constraints}

  Inference proceeds in the following steps:

  \begin{enumerate}
  \item Infer where regions goes
  \item Turn the type, linearity and escape checks into constraints
  \item Solve the constraints
  \item Simplify the resulting types
  \end{enumerate}
\end{frame}

% \begin{frame}[fragile]
%   \frametitle{Inference in action}
%   \begin{onlyenv}<1>%
% \begin{minted}[texcomments=true]{OCaml}
% let average db subjects = 
%   List.map (Dbm.find db) subjects / List.length subjects

% let main () =
%   let gradeDB = ... in
%   let avg = average &gradeDB ["math";"compsci";...] in
%   Dbm.add &!gradeDB "average" avg
% \end{minted}
%   \end{onlyenv}%
%   \begin{onlyenv}<2>%
% \begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
% let average db subjects =
%   List.map (Dbm.find db) subjects / List.length subjects

% let main () =
%   let gradeDB = ... in
%   let avg = #\tikzcoord{R1}#{| average &gradeDB ["math";"compsci";...] |}#\tikzcoord{R2}# in
%   #\tikzcoord{R3}#{| Dbm.add &!gradeDB "average" avg |}#\tikzcoord{R4}#
% \end{minted}
%   \end{onlyenv}%
%   \begin{tikzpicture}[remember picture,overlay]%
%     \begin{onlyenv}<2>
%       \node[code,rounded corners=0,color=red,fit=(R1) (R2)] (RA) {};
%       \node[code,rounded corners=0,color=yellow,fit=(R3) (R4)] (RB) {};
%     \end{onlyenv}
%   \end{tikzpicture}%
% \end{frame}

\begin{frame}[fragile,shrink]
  \frametitle{Inference in action}
  \begin{center}
    \begin{tikzpicture}
      \node[annot,text width=11.5cm,scale=0.5] at (180:5) (S1) {%
\begin{minted}[texcomments=true]{OCaml}
let average db subjects = 
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = average &gradeDB ["math";"compsci";...] in
  Dbm.add &!gradeDB "average" avg
\end{minted}
      };

      \node[annot,text width=12cm,scale=0.5] at (108:3) (S2) {%
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let average db subjects =
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = #\tikzcoord{R1}#{| average &gradeDB ["math";"compsci";...] |}#\tikzcoord{R2}# in
  #\tikzcoord{R3}#{| Dbm.add &!gradeDB "average" avg |}#\tikzcoord{R4}#
\end{minted}
        \tikz[remember picture,overlay]{
          \node[code,rounded corners=0,color=red,fit=(R1) (R2)] (RA) {};
          \node[code,rounded corners=0,color=yellow,fit=(R3) (R4)] (RB) {};
        }%
      };

      \node[annot] at (36:4) (S3) {
        CONTRAINTES
      };

      \node[annot] at (-36:4) (S4) {
        SCHEMES
      };

      \node[annot] at (-108:3) (S5) {
        SIMPLIFIED SCHEMES
      };

      \draw[link,->] (S1) to[bend left] node[midway] {Infer regions} (S2) ;
      \draw[link,->] (S2) to[bend left] node[midway] {Convert into constraints} (S3);
      \draw[link,->] (S3) to[bend left] node[midway] {Solve constraints} (S4);
      \draw[link,->] (S4) to[bend left] node[midway] {Simplify types} (S5);
    \end{tikzpicture}
  \end{center}

\end{frame}
\section*{Conclusion}
